### 2020-02-04 manuscript/bef_stability/manuscript.Rmd
Add coefficient table + new richness sem

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

@@

# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin 
  )

@@

$$
S_i = 10^(\beta_0) \times 10^(\beta_R\Log(x_{Ri})) * 10^(\epsilon_{ij})
$$

@@

```{r mod-div-total}
library(lme4)
ctrl <- lmeControl(opt='optim')
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
#If we want that the model converges with basin as random slope,
# we have to remove basin with low data
sem_data %>% group_by(basin) %>% summarise(n())
stab_div_mod <- lmer(
  data = sem_data,
  control = ctrl_lmer,
  formula = log_stab ~ log_rich + (1 | basin)
)

stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
#stab_div_colin <- car::vif(stab_div_mod) not use if one response
stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggpredict(stab_div_mod, terms = c("log_rich"), type = "fe")
stab_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich = x,
    basin = group
  )

@@

```{r mod-div-troph, fig.show = "hide"}
stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
  formula = log_stab ~ log_rich + troph_group + log_rich:troph_group + (1 | basin)
  #control = ctrl
)
mySumm2 <- function(.) {
  c(beta=fixef(.),sigma=sigma(.), sig01=sqrt(unlist(VarCorr(.))))
}
stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
#plot(test,index=2)
stab_troph_ci <- confint(test)

@@

pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich", "troph_group"), type = "fe")
plot(pred_troph_mod, add.data = TRUE)
stab_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich = x,
    troph_group = group
  )

@@

bm_troph_mod <- lme(data = na.omit(stab_div_troph),
  fixed = log_bm ~ log_rich * troph_group,
  random = ~ 1 + log_rich * troph_group | basin,
  control = ctrl 
)

@@

```{r}

# Compute SEMs
stab_sem <- compute_stab_sem(.data = sem_data,
  random_effect = as.formula("~1|basin"))

@@

library(ggraph)
p_stab_sem <- ggpiecewisesem(stab_sem)
p_bm_sem <- ggpiecewisesem(bm_sem)
```

@@

```{r p-s-div}
lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
lim_log_rich <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich")
# Plot left  
p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich, y = log_stab))+
  geom_point() +
  ylim(lim_log_stab) +
  xlim(lim_log_rich) +
  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
  geom_line(data = stab_div_pred) +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
    parse = TRUE)

@@

@@

>>>>

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

@@

# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin 
  )
```

@@

$$
S_i = 10^(\beta_0) \times 10^(\beta_R\Log(x_{Ri})) \times 10^(\epsilon_{ij})
$$

$$
S_i = 10^(\beta_{0}) \times x_{Ri}10^(\beta_{R}) \times 10^(\epsilon_{ij})
$$

@@

```{r mod-div-total}
library(lme4)
ctrl <- lmeControl(opt='optim')
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
stab_div_mod <- lmer(
  data = sem_data,
  control = ctrl_lmer,
  formula = log_stab ~ log_rich + (1 | basin)
)
stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
#stab_div_colin <- car::vif(stab_div_mod) not use if one response
stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggpredict(stab_div_mod, terms = c("log_rich"), type = "fe")
stab_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich = x,
    basin = group
  )
stab_div_pred %<>%
  mutate(
    stab = 10^log_stab, # FALSE
    rich = 10^log_rich,
    cl10 =  10^conf.low,
    ch10 =  10^conf.high
  )

@@

```{r mod-div-troph, fig.show = "hide"}
stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
  formula = log_stab ~ log_rich + troph_group + log_rich:troph_group + (1 | basin)
  #control = ctrl
)
mySumm2 <- function(.) {
  c(beta=fixef(.),sigma=sigma(.), sig01=sqrt(unlist(VarCorr(.))))
}
stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
stab_troph_ci <- confint(stab_troph_boot)

@@

pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich", "troph_group"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich = x,
    troph_group = group
  )

@@

bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
  #fixed = log_bm ~ log_rich * troph_group,
  formula = log_bm ~ log_rich + troph_group + log_rich:troph_group + (1 | basin)
  #random = ~ 1 + log_rich * troph_group | basin,
  #control = ctrl 
)
bm_troph_boot <- bootMer(bm_troph_mod, mySumm2, nsim = 100)
bm_troph_ci <- confint(bm_troph_boot)

@@

```{r}
# Compute SEMs
stab_sem <- compute_stab_sem(.data = sem_data,
  random_effect = as.formula("~1|basin"))
stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

@@

library(ggraph)
p_stab_sem <- ggpiecewisesem(stab_sem)
p_bm_sem <- ggpiecewisesem(bm_sem)
p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
```

@@

```{r p-s-div}
lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
lim_log_rich <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich")
# Plot left

p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich, y = log_stab))+
  geom_point() +
  ylim(lim_log_stab) +
  xlim(lim_log_rich) +
  #scale_y_log10() +
  #scale_x_log10() +
  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
    parse = TRUE)

@@

## Model summary and diagnostics

### Biomass and stability models

```{r tab-coeff-bm, fig.cap = "Coefficient"}
# Replacement rules for term
rp_est <- c(
  "(Intercept)" =     "intercept",
  "sd\\_\\(intercept\\)\\.basin" = "sd intercept basin",
  "log_rich" =     "Median richness (log base 10)",
  "troph_group3" =     "high trophic group",
  "log_rich:troph_group3" =     "Median richness (log10) : high trophic group",
  "sig01.basin" =     "sd intercept basin",
  "sd_Observation.Residual" =     "residuals",
  "sigma" = "residuals"
)
# Replacement rules for group
rp_group <- c(
  "fixed" = "Fixed",
  "basin" = "Random"
)

```{r}
test <- map2_dfr(list(bm_troph_ci, stab_troph_ci), list(bm_troph_mod, stab_troph_mod),
  clean_summary_mod, term_rp = rp_est, group_rp = rp_group)

kable(test) %>%
  pack_rows("Biomass", 1, 6) %>%
  pack_rows("Stab", 7, 12)
```

```{r tab-coeff-stab}

## Model residuals

### Biomass and stability models

@@

### SEM linear relationship

```{r}
```

## Relationship at the absolute scale, i.e. not the logarythme scale

```{r}
ggplot(sem_data, aes(x = richness_med, y = biomass_stab)) +
  geom_point()
test <- tibble(
  richness_med = seq(1,20, length.out = 100),
  biomass_stab =
    10^(fixef(stab_div_mod)[1])*richness_med^fixef(stab_div_mod)[2]
)  
```

### 2020-02-04 report/05-stability.Rmd
Add coefficient table + new richness sem

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
myload(hab_type, habitat_pressure, dir = mypath("report"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
stab_div_troph <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) 
```

@@

ratio_bm <- net_troph_group %>%
  select(station, troph_group, biomass_avg) %>%
  spread(troph_group, biomass_avg) %>%
  mutate(bm_h_m = `3` / (`3` + `2`)) %>%
  select(station, bm_h_m)

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
myload(hab_type, habitat_pressure, dir = mypath("report"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
select <- dplyr::select
stab_div_troph <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) 
```

@@

ratio_bm <- net_troph_group %>%
  select(station, troph_group, biomass_avg) %>%
  spread(troph_group, biomass_avg) %>%
  mutate(bm_h_m = `3` / (`2` + `3`)) %>%
  select(station, bm_h_m)

ratio_bm %>%
  left_join(select(temporal_community_metrics, station, biomass_stab)) %>%
  ggplot(aes(x = bm_h_m, y = biomass_stab)) +
  geom_point() +
  scale_x_log10()
